---
title: "Spotify Wrapped"
author: "Julie Deckers"
date: "2/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, echo = FALSE)
```



For my corpus I would like to compare my Spotify Wrapped playlist to my friends and familys Wrapped playlitst. The reason I chose this is because I think that a lot of people like the Wrapped playlists and its a fun way to see what you listened to the previous year. I also think it's interesting to see if the playlists are accurate and if the persons actually listened to the songs in it. I think it's fun to just see what I listened to and what my friends listend to, and what the difference is. 
I have 2 Wrapped playlists to compare to mine. I know mine has a lot of pop music in it, so I expect it will have a lot of songs in it with a fast tempo and a high valence. One of my friends, Hemke, listened to a few artists that i also listened to, so i expect ours will have some similair features. My other friend, Fleur, listens to more rap music, so i expect hers to have al lot of energy and maybe danceability. Fleur has a lot of songs in her playlist that I dont know, so i think it will be interessting to see how it compares to mine and Hemke's playlists. I expect it will be quite different to ours. We all listen to music only in Spotify, so I think the information that i get from the playlists will be accurate.

in this plot you can see all three playlist are actually very similair. Fleur's playlist does have a bit more danceability but not a lot. My playlist has the least energy. I would say Hemke's playlist sit in between mine and Fleur's playlist.



```{r}
library(tidyverse)
library(spotifyr)

Julie <- get_playlist_audio_features("","37i9dQZF1EM27HE4pdYYcz")
Hemke <- get_playlist_audio_features("","37i9dQZF1EMgeVFiZwhb4Z")
Fleur <- get_playlist_audio_features("","37i9dQZF1EMd6LXIgrTylx")

Spotify_Wrapped <-
  bind_rows(
    Julie %>% mutate(category = "Julie"),
    Hemke %>% mutate(category = "Hemke"),
    Fleur %>% mutate(category = "Fleur")
  )


ggplot(Spotify_Wrapped,aes(x=valence,y=danceability,color=category,size=energy)) + geom_point() +ggtitle("Comparing Spotify Wrapped Playlists")










```


